\addcontentsline{toc}{chapter}{Preface \& acknowledgments}
\chapter*{Preface \& acknowledgments}

This Voice over IP (VoIP) library, JVOIPLIB, would not have become what it is
without the help of several people. The library is based upon work done for my
thesis at the `School for Knowledge Technology'\footnote{A cooperation between
the Hasselt University (\url{http://www.uhasselt.be}) and the
Maastricht University (\url{http://www.unimaas.nl}).}. So first of all,
I would like to thank prof. dr. Wim Lamotte, who assisted me with both the
thesis text and the testing of VoIP programs I made.

Many other people also assisted me with the testing of such programs. Therefore,
my gratitude also goes to: Koen Beets, Kris Luyten, Tom Van Laerhoven, Peter
Quax, Dani\"el Teunkens, Igor Kalders, Stef Cant, Panagiotis Issaris and Silvio
Sawicki. Special thanks go to Igor: thanks to him I was able to perform some
rather more `long distance' tests.

I started working on this library during my vacation, but a huge part of it
was developed later, when I was employed at the Expertise Centre for Digital Media\footnote{
\url{http://www.edm.uhasselt.be}} which is a research center of the Hasselt University. 
There, I was allowed to continue working on this library. For
this reason, I would like to thank prof. dr. Frank Van Reeth, who gave
me permission to continue my work on the library and who allowed it to
be released under the terms of the `Library General Public License' (LGPL).

I would also like to thank Kris Luyten again: the many discussions
we had about object-orientation, code structure and development in general
certainly helped to improve both my programming style and the structure of
this library.

Finally, many thanks also go to Bill Gardner and Keith Martin: thanks to 
their measurements of Head-Related Impulse Responses, I was able to make a 
decent 3D sound implementation.

